Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-04-12 publication_materials/ms_rbc.tex
stable build: bibtex implemented

\section{Introduction}
Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical settings.
% Buoyancy-driven convection regulates heat transfer and often gives way to violently turbulent flows, thereby dominating large-scale behaviors and fueling small-scale processes in important systems \cite{Couston}.

Aggressive convection, which is associated with large Rayleigh numbers $Ra$, is difficult to simulate. 
% State of the art convection simulations performed by \cite{Zhu_2018} have reached $Ra = 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
The scaling behavior of the Nusselt number $\Nu$ (nondimensionalized heat transfer) in the highly turbulent ultimate regime is of particular interest.
There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus}, \cite{Kraichnan} \cite{Spiegel}, \cite{Castaing}, \cite{Grossman}, \cite{Ahlers}, \cite{Malkus}.

@@

In \cite{Chini_sw}, researchers develop and solve a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. This is realized by defining a mean state which, hypothetically, evolves on a slow time-scale. An analytic expression for the first-order perturbations' amplitude is found by deriving a solvability condition of the second-order perturbations and integrating over the domain spatially. 
We seek to solve the Boussinesq Rayleigh–Bénard convection equations using an analogous strategy. 
The application of this procedure yields time-invariant solutions to the quasilinear problem with a range of expected and unexpected features.

@@

To derive the linearized system, we posit that each field can be represented as the sum of a mean profile (denoted by $\bar{\cdot } \;$) and a perturbation function (denoted by $\cdot'$).
\begin{align}
    \mathbf{u}(x, z, t) &= A\mathbf{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
    &= Au'(x, z, t)\hat{x} + Aw'(x, z, t)\hat{z} \\
    T(x, z, t) &= \bar{T}(z) + AT'(x, z, t) \label{EQ:reynolds_dc_T}\\
    p(x, z, t) &= \bar{p}(z) + Ap'(x, z, t).
\end{align}
where $A$ is some unknown real amplitude and the normalization
\begin{equation}
    \int_{-\frac{1}{2}}^{\frac{1}{2}} \big| \theta (z) \big| dz = 1
\end{equation}
is specified for completion.
Upon substitution, we equate terms which scale linearly with the perturbations, yielding the linearized stability equations
\begin{align}
    \nabla \cdot \mathbf{u'} &= 0 \label{EQ:linear1}\\
    \frac{\partial\mathbf{u'}}{\partial t} &= - \nabla p' + T'\hat{z} + \mathcal{R} \nabla^2 \mathbf{u'} \label{EQ:linear2}\\
    \frac{\partial T'}{\partial t} + \frac{\partial \bar{T}}{\partial z} w' &= \mathcal{P} \nabla^2 T' \label{EQ:linear3}
\end{align}
with Dirichlet boundary conditions 
\begin{equation}
    T'|_{z = \pm \frac{1}{2}} = 0, \quad u'|_{z = \pm \frac{1}{2}} = 0, \quad p'|_{z = \pm \frac{1}{2}} = 0.
\end{equation}
In 1916, Lord Rayleigh observed that (\ref{EQ:linear1}) and (\ref{EQ:linear3}) can be manipulated into a separable form with generalized solutions
\begin{align}
    w'(x, z, t) &= W(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes1}\\ 
    u'(x, z, t) &= U(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes2}\\ 
    T'(x, z, t) &= \theta(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes3}\\ 
    p'(x, z, t) &= P(z) \, e^{i(k_xx-st)}\label{EQ:normal_modes4}
\end{align}
where $s = \sigma + i\omega$ and $k_x$ is constrained, by periodicity, to the countably infinite set (spectrum) of wavenumbers
\begin{align}
    k_x \in \big\{\frac{n\pi}{2} \, \big| \, n \in \mathbb{N}\big\}.
\end{align}
For each $k_x$, we can assess the stability of the perturbations by solving for the eigenvalue $s$, whose imaginary component $\omega$ plays the role of an exponential growth rate. 
Solution yields a finite set of eigenvalues, among which, that with maximum $\omega$ is assumed to be dominant. 
Positive eigenvalues indicate that the system is unstable to small disturbances of wavenumber $k_x$, while negative eigenvalues indicate stability. 
A complete linear stability analysis requires solution over the full spectrum of wavenumbers. 
The prototypical case is used to demonstrate that the critical Rayleigh number $Ra_c = 1708$ when $\frac{\partial \bar{T}}{\partial z} = -1$.

@@

\section{Perturbation Evolution}
Solving the linearized system (\ref{EQ:linear1}) -- (\ref{EQ:linear3}) does not yield $A^2$. 
To evolve $\bar{T}$ numerically, we assume the perturbations and mean quantities depend on different time-scales, as in \cite{Chini_sw}. On the fast time-scale, stable modes will decay and unstable modes will act according to (\ref{EQ:T0_IVP}). 
We make the ansatz that only marginally stable modes will affect $\bar{T}$ on long time-scales
\begin{equation}
    \max_{k_x} \{ \omega \} = 0
\end{equation}
thereby constraining $A^2$ at each timestep.

@@

The most resilient and unexpected feature of thermally equilibrated mean temperature profiles are the pronounced dips adjacent to the boundary layers. 
These dips appear in every solution, regardless of $Ra$. 
Physically, they correspond to thin layers in which the temperature gradient reverses, contradicting a hypothesis of \cite{Malkus_1954}. 
This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}.  
\begin{figure}
    \centering
    \includegraphics[width=3.4in]{T_profs_na.png}
    \caption{mean temperature profiles $\bar{T}$ for $Ra = 10^8$. 
    The initial profile is given by (\ref{EQ:T0}). 
    The equilibrated curve refers to the mean temperature profile of the marginally-stable thermally-equilibrated state. 
    The simulation profile is obtained by performing a 2-dimensional nonlinear simulation with \texttt{Dedalus} until thermal and kinetic relaxation. 
    The simulation temperature data are horizontally- and time-averaged. 
    The initial, equilibrated, and simulation profiles have increasingly relaxed boundary regions (respectively). 
    The equilibrated profile exhibits prominent dips, nested alongside the boundary regions. 
    The purpose of this feature is not well understood.}
    \label{fig:T0_profiles}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=3.4in]{kx_m_ra1.png}
    \caption{Wavenumbers of marginally-stable modes of thermally equilibrated states. 
    Markers are color-coded according to their adjacent local maxima index in the eigenvalue spectrum. 
    For example, the spectrum corresponding to $Ra = 10^5$ has marginal wavenumbers $k_x = \pi, \, 1.5\pi$ adjacent to a presumed local maximum between these two allowed values. 
    The $Ra = 10^9$ spectrum, shown in lower right corner of Figure \ref{fig:flux}, has three presumed local maxima, with a single marginal mode adjacent to the first maximum ($k_x = 1.5\pi$), two marginal modes adjacent to the second maximum ($k_x = 6\pi, \, 6.5\pi$), and two marginal modes adjacent to the third maximum ($k_x = 23.5\pi, \, 24\pi$). 
    The largest wavenumbers of the green branch obey a power-law relationship with $Ra$}
    \label{fig:kx_marginals}
\end{figure}
\begin{figure*}
    \centering
    \begin{tabular}{@{}c@{}}
        \includegraphics[width=3.4in]{flux_sup_n.png}
    \end{tabular}
    \begin{tabular}{@{}c@{}}
        \includegraphics[width=3.4in]{EV_spectra_2ra.png}
    \end{tabular}
    \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states $Ra = 2 \times 10^5$ (top) and $Ra = 10^9$ (bottom). 
    Advection profiles belong to marginally-stable modes. 
    For low $Ra$, a single mode with $k_x = 1.5\pi$ is sufficient to oppose boundary layer diffusion and facilitate heat flux throughout the bulk of the domain. 
    For large $Ra$, high-wavenumber modes contribute pronounced small-scale advection profiles which tightly hug the thin boundary layers. 
    A combination of of progressively wider advection profiles is necessary to transition to the $k_x = 1.5\pi$ mode.}
    \label{fig:flux}
\end{figure*}
\begin{figure*}
    \centering
    \includegraphics[width=7.1in]{nu_ra.PNG}
    \caption{Nusselt numbers are shown for marginally-stable thermally-equilibrated states, statistically-steady direct numerical simulations performed with \texttt{Dedalus} \cite{Anders_cd}, and equilibrated nonlinear solutions, which maximize heat flux, given by \cite{Waleffe}. 
    Both obey power-law relationships with $Ra$, with $Ra \sim \Nu^3$ in agreement with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} as well as \cite{Malkus}. 
    Marginally-stable states' Nusselt numbers exceed simulation Nusselt numbers. 
    This can be well explained by the contrasting boundary region geometries shown in Figure \ref{fig:T0_profiles}.}%
    \label{fig:nu_vs_ra}%
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics[width=3.4in]{del_ra.PNG}
    \caption{Boundary layer widths $\delta$ of marginally-stable thermal equilibria. 
    We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}. 
    Plotting on a log-log scale, we find $\delta$ and $Ra$ obey a power-law relationship. We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ implying $Ra \propto  \delta^{-3}$, as predicted by \cite{Malkus}}
    \label{fig:bl_ra}
\end{figure}

@@

Nusselt numbers $\Nu$ of various solutions are given in Figure \ref{fig:nu_vs_ra}. 
The marginally-stable thermally-equilibrated states and numerical simulation data exhibit power-law relationships with $Ra$. 
More specifically, $Ra \sim \Nu^3$ which agrees with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} and the scaling argument given by \cite{Malkus}. 
The nonlinear solutions, which maximize heat flux, are obtained by \cite{Waleffe}. 
$\Nu$ of both equilibria exceed that of simulations, which might be due to the transitional behaviors outlined by \cite{Yalniz} and \cite{Cvitanovic} inhibiting heat flux. 
Alternatively, we might anticipate the existence of exact coherent states with smaller $\Nu$, forming another node in the Markov chain whose long-term behavior agrees with the simulation data.

@@

        \caption{Nusselt numbers of simulations performed at $Ra \, = \, 10^8$ with conventional initial conditions (red) and marginally-stable thermally-equilibrated initial conditions (blue). 
        Simulations run with thermally-equilibrated states do not undergo a convective-transient period because the characteristic plume structure exists on initialization. 

@@

\section{Discussion}\label{sec:Discussion}
In general, the reduced model we study in this paper can be perceived as a unique way to describe Rayleigh–Bénard convection. 
Solutions to the quasilinear problem retain several key features that are ubiquitous in experiments and simulations: power-law $\Nu$ scaling, plume-like structures, and minimum length-scale approximations \cite{Malkus}. 
They also exhibit unique and unexpected features: gradient-reversal/dips in temperature profiles, kinetic exaggeration, and greater $\Nu$ than other time-invariant solutions. 
We also obtain indistinguishable solutions despite initializing with different mean temperature profiles $\bar{T}$. 
Thus solutions might be unique, but we cannot demonstrate this rigorously.

@@

\begin{thebibliography}{99}

\bibitem{Zhu} Xiaojue Zhu, Varghese Mathai, Richard J. A. M. Stevens, Roberto Verzicco, and Detlef Lohse (2018). Transition to the Ultimate Regime in Two-Dimensional Rayleigh-Bénard Convection. Phys. Rev. Lett. 120, 144502

\bibitem{Malkus} Malkus W. V. R. 1954 The heat transport and spectrum of thermal turbulenceProc. R. Soc. Lond. A225196–212

\bibitem{Howard} Howard L.N. (1966) Convection at high Rayleigh number. In: Görtler H. (eds) Applied Mechanics

\bibitem{Chini_la} Chini, G., Malecha, Z., \& Dreeben, T. (2014). Large-amplitude acoustic streaming. Journal of Fluid Mechanics, 744, 329-351. doi:10.1017/jfm.2014.61

\bibitem{Chini_sw} Michel, G., \& Chini, G. (2019). Strong wave–mean-flow coupling in baroclinic acoustic streaming. Journal of Fluid Mechanics, 858, 536-564. doi:10.1017/jfm.2018.785

\bibitem{Shishkina} Olga Shishkina, Susanne Horn, Sebastian Wagner, Phys. Rev. Lett. 114

\bibitem{Anders_cd} Evan H. Anders, Geoffrey M. Vasil, Benjamin P. Brown, and Lydia Korre Phys. Rev. Fluids 5, 083501

\bibitem{Waleffe} Waleffe F., Boonkasame A., Smith L.M. Heat transport by coherent Rayleigh–Bénard convection Phys. Fluids, 27 (2015), Article 051702

\bibitem{Yalniz} Yalnız, Gökhan; Hof, Björn; Burak Budanur, Nazmi. Coarse graining the state space of a turbulent flow using periodic orbits

\bibitem{Ossendrijver} The solar dynamo. Ossendrijver, M. The Astron. Astrophys. Rev. 11, 287–367 (2003).

\bibitem{Kraichnan} Kraichnan, R. Turbulent Thermal Convection at Arbitrary Prandtl Number (1962). https://doi.org/10.1063/1.1706533

% \bibitem{Featherstone} The Spectral Amplitude of Stellar Convection and its Scaling in the High-Rayleigh-Number Regime. Featherstone, N. A., \& Hindman, B. W. (2016). The Astrophysical Journal, 818, 32–45.

\bibitem{chini_cells} Large Rayleigh number thermal convection: heat flux predictions and strongly nonlinear solutions. Chini, G. P., \& Cox, S. M. (2009). Physics of Fluids, 21, doi:10.1063/1.3210777

\bibitem{Sondak} Sondak, D., Smith, L., \& Waleffe, F. (2015). Optimal heat transport solutions for Rayleigh–Bénard convection. Journal of Fluid Mechanics, 784, 565-595. doi:10.1017/jfm.2015.615

% scaling review
\bibitem{Grossman} Grossman, S., \& Lohse, D. (2000). Scaling in thermal convection: A unifying theory. Journal of Fluid Mechanics, 407, 27-56. doi:10.1017/S0022112099007545

% modal convection: scaling
\bibitem{Spiegel} Thermal Turbulence at Very Small Prandtl Number. Spiegel, E. (1962) Journal of Geophysical Research, https://doi.org/10.1029/JZ067i008p03063

\bibitem{Castaing} Castaing, B. et al. (1988) Scaling of hard Thermal Turbulence in Rayleigh-B\'enard Convection

\bibitem{Ahlers} Ahlers, G. Heat transfer \& large-scale dynamics in turbulent Rayleigh-B´enard convection

\bibitem{Shraiman} Shraiman BI, Siggia ED. Heat transport in high-Rayleigh-number convection. Phys Rev A. 1990 Sep 15;42(6):3650-3653. doi: 10.1103/physreva.42.3650. PMID: 9904456.

\bibitem{Wen} Wen, B., Goluskin, D., Doering, C. (2020) Steady Rayleigh–B´enard convection between no-slip boundaries

\bibitem{Cvitanovic} P Cvitanovic and J F Gibson (2010). Geometry of the turbulence in wall-bounded shear flows: periodic orbits. http://dx.doi.org/10.1088/0031-8949/2010/T142/014007

\bibitem{Couston} Couston, L.A., Lacoanet, D., Favier, B., Bars, M. (2019). Shape and size of large-scale vortices: a universal fluid pattern in geophysical dynamics

\end{thebibliography}

% \bibliographystyle{plain}
% \bibliography{he}

>>>>

\section{Introduction}
Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical settings.
Buoyancy-driven convection regulates heat transfer and often gives way to violently turbulent flows, thereby dominating large-scale behaviors and fueling small-scale processes in important systems \cite{Couston}.

Aggressive convection, which is associated with large Rayleigh numbers $Ra$, is difficult to simulate. 
State of the art convection simulations performed by \cite{Zhu_2018} have reached $Ra = 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
The scaling behavior of the Nusselt number $\Nu$ (nondimensionalized heat transfer) in the highly turbulent ultimate regime is of particular interest.
There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus_1954}, \cite{Howard_1966}, \cite{Kraichnan} \cite{Spiegel}, \cite{Castaing}, \cite{Grossman}, \cite{Ahlers}.

@@

In \cite{michel_chini_2019}, researchers develop and solve a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. This is realized by defining a mean state which, hypothetically, evolves on a slow time-scale. An analytic expression for the first-order perturbations' amplitude is found by deriving a solvability condition of the second-order perturbations and integrating over the domain spatially. 
We seek to solve the Boussinesq Rayleigh–Bénard convection equations using an analogous strategy. 
The application of this procedure yields time-invariant solutions to the quasilinear problem with a range of expected and unexpected features.

@@

To derive the quasilinear form, we posit that each field can be represented as the sum of a mean profile (denoted by $\bar{\cdot } \;$) and a perturbation function (denoted by $\cdot'$).
\begin{align}
    \mathbf{u}(x, z, t) &= A(t) \mathbf{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
    &= A(t) u'(x, z, t)\hat{x} + A(t) w'(x, z, t)\hat{z} \\
    T(x, z, t) &= \bar{T}(z) + A(t) T'(x, z, t) \label{EQ:reynolds_dc_T}\\
    p(x, z, t) &= \bar{p}(z) + A(t) p'(x, z, t).
\end{align}
where $A(t)$ is some unknown real amplitude and the mean-velocity components vanish due to incompressibility and symmetry. We require that perturbations have no horizontal-average, i.e. an arbitrary perturbation $f'$ obeys
\begin{equation}
    \langle f'(x, z, t) \rangle_x \equiv \int_{0}^4 f'(x, z, t) dx = 0.
\end{equation}
Assuming the existance of nontrivial solutions, we also fix the volume-average
\begin{equation}
  \langle \langle T'^2 \rangle_x \rangle_z = 1
\end{equation}
thereby constraining $A(t)$. 
Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) yields

Upon substitution, we equate terms which scale linearly with the perturbations, yielding the linearized stability equations
\begin{align}
    \nabla \cdot \mathbf{u'} &= 0 \label{EQ:linear1}\\
    \frac{\partial\mathbf{u'}}{\partial t} &= - \nabla p' + T'\hat{z} + \mathcal{R} \nabla^2 \mathbf{u'} \label{EQ:linear2}\\
    \frac{\partial T'}{\partial t} + \frac{\partial \bar{T}}{\partial z} w' &= \mathcal{P} \nabla^2 T' \label{EQ:linear3}
\end{align}
with Dirichlet boundary conditions 
\begin{equation}
    T'|_{z = \pm \frac{1}{2}} = 0, \quad u'|_{z = \pm \frac{1}{2}} = 0, \quad p'|_{z = \pm \frac{1}{2}} = 0.
\end{equation}
In 1916, Lord Rayleigh observed that (\ref{EQ:linear1}) and (\ref{EQ:linear3}) can be manipulated into a separable form with generalized solutions
\begin{align}
    w'(x, z, t) &= W(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes1}\\ 
    u'(x, z, t) &= U(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes2}\\ 
    T'(x, z, t) &= \theta(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes3}\\ 
    p'(x, z, t) &= P(z) \, e^{i(k_xx-st)}\label{EQ:normal_modes4}
\end{align}
where $s = \sigma + i\omega$ and $k_x$ is constrained, by periodicity, to the countably infinite set (spectrum) of wavenumbers
\begin{align}
    k_x \in \big\{\frac{n\pi}{2} \, \big| \, n \in \mathbb{N}\big\}.
\end{align}
For each $k_x$, we can assess the stability of the perturbations by solving for the eigenvalue $s$, whose imaginary component $\omega$ plays the role of an exponential growth rate. 
Solution yields a finite set of eigenvalues, among which, that with maximum $\omega$ is assumed to be dominant. 
Positive eigenvalues indicate that the system is unstable to small disturbances of wavenumber $k_x$, while negative eigenvalues indicate stability. 
A complete linear stability analysis requires solution over the full spectrum of wavenumbers. 
The prototypical case is used to demonstrate that the critical Rayleigh number $Ra_c = 1708$ when $\frac{\partial \bar{T}}{\partial z} = -1$.

@@

\section{Perturbation Evolution}
Solving the linearized system (\ref{EQ:linear1}) -- (\ref{EQ:linear3}) does not yield $A^2$. 
To evolve $\bar{T}$ numerically, we assume the perturbations and mean quantities depend on different time-scales, as in \cite{michel_chini_2019}. On the fast time-scale, stable modes will decay and unstable modes will act according to (\ref{EQ:T0_IVP}). 
We make the ansatz that only marginally stable modes will affect $\bar{T}$ on long time-scales
\begin{equation}
    \max_{k_x} \{ \omega \} = 0
\end{equation}
thereby constraining $A^2$ at each timestep.

@@

The most resilient and unexpected feature of thermally equilibrated mean temperature profiles are the pronounced dips adjacent to the boundary layers. 
These dips appear in every solution, regardless of $Ra$. 
Physically, they correspond to thin layers in which the temperature gradient reverses, contradicting a hypothesis of \cite{Malkus_1954}. 
This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}.  
\begin{figure}
    \centering
    \includegraphics[width=3.4in]{T_profs_na.png}
    \caption{mean temperature profiles $\bar{T}$ for $Ra = 10^8$. 
    The initial profile is given by (\ref{EQ:T0}). 
    The equilibrated curve refers to the mean temperature profile of the marginally-stable thermally-equilibrated state. 
    The simulation profile is obtained by performing a 2-dimensional nonlinear simulation with \texttt{Dedalus} until thermal and kinetic relaxation. 
    The simulation temperature data are horizontally- and time-averaged. 
    The initial, equilibrated, and simulation profiles have increasingly relaxed boundary regions (respectively). 
    The equilibrated profile exhibits prominent dips, nested alongside the boundary regions. 
    The purpose of this feature is not well understood.}
    \label{fig:T0_profiles}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=3.4in]{kx_m_ra1.png}
    \caption{Wavenumbers of marginally-stable modes of thermally equilibrated states. 
    Markers are color-coded according to their adjacent local maxima index in the eigenvalue spectrum. 
    For example, the spectrum corresponding to $Ra = 10^5$ has marginal wavenumbers $k_x = \pi, \, 1.5\pi$ adjacent to a presumed local maximum between these two allowed values. 
    The $Ra = 10^9$ spectrum, shown in lower right corner of Figure \ref{fig:flux}, has three presumed local maxima, with a single marginal mode adjacent to the first maximum ($k_x = 1.5\pi$), two marginal modes adjacent to the second maximum ($k_x = 6\pi, \, 6.5\pi$), and two marginal modes adjacent to the third maximum ($k_x = 23.5\pi, \, 24\pi$). 
    The largest wavenumbers of the green branch obey a power-law relationship with $Ra$}
    \label{fig:kx_marginals}
\end{figure}
\begin{figure*}
    \centering
    \begin{tabular}{@{}c@{}}
        \includegraphics[width=3.4in]{flux_sup_n.png}
    \end{tabular}
    \begin{tabular}{@{}c@{}}
        \includegraphics[width=3.4in]{EV_spectra_2ra.png}
    \end{tabular}
    \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states $Ra = 2 \times 10^5$ (top) and $Ra = 10^9$ (bottom). 
    Advection profiles belong to marginally-stable modes. 
    For low $Ra$, a single mode with $k_x = 1.5\pi$ is sufficient to oppose boundary layer diffusion and facilitate heat flux throughout the bulk of the domain. 
    For large $Ra$, high-wavenumber modes contribute pronounced small-scale advection profiles which tightly hug the thin boundary layers. 
    A combination of of progressively wider advection profiles is necessary to transition to the $k_x = 1.5\pi$ mode.}
    \label{fig:flux}
\end{figure*}
\begin{figure*}
    \centering
    \includegraphics[width=7.1in]{nu_ra.PNG}
    \caption{Nusselt numbers are shown for marginally-stable thermally-equilibrated states, statistically-steady direct numerical simulations performed with \texttt{Dedalus} \cite{Anders_cd}, and equilibrated nonlinear solutions, which maximize heat flux, given by \cite{Waleffe}. 
    Both obey power-law relationships with $Ra$, with $Ra \sim \Nu^3$ in agreement with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} as well as \cite{Malkus_1954}. 
    Marginally-stable states' Nusselt numbers exceed simulation Nusselt numbers. 
    This can be well explained by the contrasting boundary region geometries shown in Figure \ref{fig:T0_profiles}.}%
    \label{fig:nu_vs_ra}%
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics[width=3.4in]{del_ra.PNG}
    \caption{Boundary layer widths $\delta$ of marginally-stable thermal equilibria. 
    We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}. 
    Plotting on a log-log scale, we find $\delta$ and $Ra$ obey a power-law relationship. We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ implying $Ra \propto  \delta^{-3}$, as predicted by \cite{Malkus_1954}}
    \label{fig:bl_ra}
\end{figure}

@@

Nusselt numbers $\Nu$ of various solutions are given in Figure \ref{fig:nu_vs_ra}. 
The marginally-stable thermally-equilibrated states and numerical simulation data exhibit power-law relationships with $Ra$. 
More specifically, $Ra \sim \Nu^3$ which agrees with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} and the scaling argument given by \cite{Malkus_1954}. 
The nonlinear solutions, which maximize heat flux, are obtained by \cite{Waleffe}. 
$\Nu$ of both equilibria exceed that of simulations, which might be due to the transitional behaviors outlined by \cite{Yalniz} and \cite{Cvitanovic} inhibiting heat flux. 
Alternatively, we might anticipate the existence of exact coherent states with smaller $\Nu$, forming another node in the Markov chain whose long-term behavior agrees with the simulation data.

@@

        \caption{Nusselt numbers of simulations performed at $Ra = 10^8$ with conventional initial conditions (red) and marginally-stable thermally-equilibrated initial conditions (blue). 
        Simulations run with thermally-equilibrated states do not undergo a convective-transient period because the characteristic plume structure exists on initialization.}

@@

\section{Discussion}\label{sec:Discussion}
In general, the reduced model we study in this paper can be perceived as a unique way to describe Rayleigh–Bénard convection. 
Solutions to the quasilinear problem retain several key features that are ubiquitous in experiments and simulations: power-law $\Nu$ scaling, plume-like structures, and minimum length-scale approximations \cite{Malkus_1954}. 
They also exhibit unique and unexpected features: gradient-reversal/dips in temperature profiles, kinetic exaggeration, and greater $\Nu$ than other time-invariant solutions. 
We also obtain indistinguishable solutions despite initializing with different mean temperature profiles $\bar{T}$. 
Thus solutions might be unique, but we cannot demonstrate this rigorously.

@@

% \bibliographystyle{plain}
\bibliography{he}
